### 2008-09-18 doc/client/client_technical.tex
Job description class documentation update

The {\JobDescription} class has tree back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern match
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.

>>>>

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern match
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.

Parsing is currently possible from any of the languages but output
generation is only partially supported. Only JSDL and JDL output
generation is implemented yet and even for these there are some
limitations.

The conversion mainly means a syntactial transformation and the
{\JobDescription} class can of course do nothing in those cases where
not enough data to assemble a given attribute is available or when
information can be lost because the received attribute has no
equivalent in the output language.

For the JSDL output generation the {\JobDescription} class is using
the core JSDL's capabilities amended with the JSDL-POSIX and JSDL-ARC
extensions. The loss of information is minimal in case of generating
such an output.

For the JDL generation the latest version of JDL specification was
used (v0.9) \cite{jdl}. Deprecated and backward compatibility
attributes are not implemented.

No XRSL output generation is implemented yet.
